Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2014-10-30 Papers/InProgress/LogicAndReligionCongress/Abstract.tex
Improve Hajek's appendix

%\section{Anderson's Emendation (cf. Appendix \ref{apx:Anderson})}

@@

For both \textbf{constant domain semantics} and \textbf{varying domain
semantics}, the following results hold for \emph{Anderson's
Emendation} (cf. Appendix \ref{apx:Anderson}):  % the theorems T1, C
and T3' can be quickly automated (in logics \K, \K and \KB,
respectively); % the axioms A4 and A5 are proven redundant\footnote{
An axiom $A$ is redundant w.r.t. a set of axioms $S$ iff $A$ is
entailed by $S$.  } (the former in logic \KFourB and the latter
already in \K); % a trivial countermodel (with two worlds and  two
individuals) for MC is generated by Nitpick (for all mentioned
logics); all axioms and definitions are shown to be mutually
consistent.

@@

\framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[H:A12] The negation of a property necessarily implied by a
  positive property is not positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp \neg P(\neg \psi)]}$$
\item[H:D1] A \emph{God-like} being necessarily possesses those and only those properties that are necessarily implied by a positive property: 
  $$\hol{G_H(x) \equiv \forall \varphi [\nec \varphi(x) \biimp \exq \psi[P(\psi) \wedge \nec \allq x [\psi(x)  \imp \varphi(x))]]}$$ 
\item[D4]  A property is positive\textsuperscript{\#} iff it is necessarily implied by a positive property: 
  $$\hol{P^\#(\varphi) \equiv \exq \psi[P(\psi) \wedge \nec \allq x[\psi(x) \imp \varphi(x)]]}$$
\item[A3']  The property of being God-like is positive: 
  $$\hol{P(G_H)}$$
\item[H:A4]  Positive\textsuperscript{\#} properties are necessarily positive\textsuperscript{\#}: 
  $$\hol{\allq \varphi [P^\#(\varphi) \imp \Box \; P^\#(\varphi)]}$$ 
\item[A:D2] An \emph{essence} of an individual is a property that necessarily implies those and only those properties that the individual has necessarily: $$\hol{\essA{\varphi}{x} \equiv \allq
  \psi [\nec \psi(x) \biimp \nec \allq y (\varphi(y) \imp \psi(y))]}$$ 
\item[D3'] \emph{Necessary existence} of an individual is the necessary exemplification of all its essences: 
  $$\hol{\NE_A(x) \equiv \allq \varphi [\essA{\varphi}{x} \imp \nec
  \exq y [\varphi(y)]]}$$
\item[H:A5] Necessary existence is a positive\textsuperscript{\#} property: $$\hol{P^\#(\NE_A)}$$ 
% 
\end{itemize}
\end{minipage}
} %\vskip-.5em

>>>>

@@

For both \textbf{constant domain semantics} and \textbf{varying domain
semantics}, the following results hold for \emph{Anderson's
Emendation} (cf. Appendix \ref{apx:Anderson}): T1, C
and T3' can be quickly automated (in logics \K, \K and \KB,
respectively); the axioms A4 and A5 are proven redundant\footnote{
An axiom $A$ is redundant w.r.t. a set of axioms $S$ iff $A$ is
entailed by $S$.  } (the former in logic \KFourB and the latter
already in \K); a trivial countermodel (with two worlds and  two
individuals) for MC is generated by Nitpick (for all mentioned
logics); all axioms and definitions are shown to be mutually
consistent.

@@

\framebox[\columnwidth][r]{
\begin{minipage}{.94\columnwidth}\small
\begin{itemize}
\item[H:A12] The negation of a property necessarily implied by a
  positive property is not positive:
  $$\hol{\allq \varphi \allq \psi [(P(\varphi) \wedge \nec \allq x [\varphi(x)
  \imp \psi(x)]) \imp \neg P(\neg \psi)]}$$
\item[D4]  A property is positive\textsuperscript{\#} iff it is necessarily implied by a positive property: 
  $$\hol{P^\#(\varphi) \equiv \exq \psi[P(\psi) \wedge \nec \allq x[\psi(x) \imp \varphi(x)]]}$$
\item[H:D1] A \emph{God-like} being necessarily possesses those and only those properties that are positive\textsuperscript{\#}: 
  $$\hol{G_H(x) \equiv \forall \varphi [P^\#(\varphi) \biimp \nec \varphi(x)]}$$ 
\item[A3']  The property of being God-like is positive: 
  $$\hol{P(G_H)}$$
\item[H:A4]  Positive\textsuperscript{\#} properties are necessarily positive\textsuperscript{\#}: 
  $$\hol{\allq \varphi [P^\#(\varphi) \imp \Box \; P^\#(\varphi)]}$$ 
\item[A:D2] An \emph{essence} of an individual is a property that necessarily implies those and only those properties that the individual has necessarily: $$\hol{\essA{\varphi}{x} \equiv \allq
  \psi [\nec \psi(x) \biimp \nec \allq y (\varphi(y) \imp \psi(y))]}$$ 
\item[D3'] \emph{Necessary existence} of an individual is the necessary exemplification of all its essences: 
  $$\hol{\NE_A(x) \equiv \allq \varphi [\essA{\varphi}{x} \imp \nec
  \exq y [\varphi(y)]]}$$
\item[H:A5] Necessary existence is a positive\textsuperscript{\#} property: $$\hol{P^\#(\NE_A)}$$ 
% 
\end{itemize}
\end{minipage}
} %\vskip-.5em
